---
title: "STAT4011_pj1_korea"
output: html_document
---

data source : https://www.kaggle.com/kimjihoo/coronavirusdataset

possible use dataset
policy, searchtrend, TimeProvince


load the required library
```{r}
library(ggplot2)
library(Metrics)
library(randomForest)
#library(plot.matrix)
#library(psych)
library(forecast)
library(xgboost)
```

set seed and read data
```{r}
set.seed(4011)
file_path = "C:/Users/cheng/OneDrive/Desktop/hw/STAT4011/STAT4011/dataset"
case =  read.csv(paste0(file_path, '/Time.csv'))
policy = read.csv(paste0(file_path, '/Policy.csv'))
search_trend = read.csv(paste0(file_path, '/SearchTrend.csv'))
province = read.csv(paste0(file_path, '/TimeProvince.csv'), stringsAsFactors = FALSE)
weather = read.csv(paste0(file_path, '/Weather.csv'), stringsAsFactors = FALSE)
timeage = read.csv(paste0(file_path, '/Timeage.csv'), stringsAsFactors = FALSE, row.names=NULL)
timegen = read.csv(paste0(file_path, '/TimeGender.csv'), stringsAsFactors = FALSE, row.names=NULL)
```

arima
```{r, fig.width = 8, fig.height = 5}
confirm_ts = as.ts(case$confirmed)
plot(confirm_ts)
#prove it is a non-seasonal data
#decompose(confirm_ts)
#auto.arima
auto.arima(confirm_ts)
par(mar=c(5.1, 4.1, 4.1, 4.1)) # adapt margins
acf(confirm_ts, lag.max = 100)
pacf(confirm_ts, lag.max = 60)
#fit arima
ts_md = arima(confirm_ts, order(c(1,0,0)))
# test
test  = Box.test(ts_md$residuals, lag = 1, type = c("Box-Pierce", "Ljung-Box"), fitdf = 0)


```


merge and plot for case, policy and search trend
```{r, fig.width = 8, fig.height = 5}
case_policy_df = merge(case, policy, by.x='date', by.y='start_date', all = TRUE)[-1,]
case_policy_search = merge(case_policy_df, search_trend, by.x='date', by.y='date')
# non cumulative
case_policy_search$confirmed = c(0, diff(case_policy_search$confirmed))
case_policy_search$test = c(0, diff(case_policy_search$test))
case_policy_search$deceased = c(0, diff(case_policy_search$deceased))
df = case_policy_search
df$policy_id = as.numeric(df$policy_id)
df$date = as.Date(df$date)
for (i in 1:nrow(df)){
  if (is.na(df$policy_id[i])) df$policy_id[i] = 0
  if(df$policy_id[i] > 0) {
    df$policy_id[i] = 1
  } else {
    df$policy_id[i] = NA
  }
}
#plot the graph
ggplot() + 
ggtitle("confirmed case against government applied policy")+
geom_line(data = df, aes(x = date, y = confirmed, color = 'confirmed')) + 
#geom_line(data = df, aes(x = date, y = deceased, color = 'deceased'))+
#geom_line(data = df, aes(x = date, y = test, color = 'test'))+
geom_point(data = df, aes(x = date, y = policy_id, color = 'government applied policy'), size = 0.01) +
ylab('')

#ggplot() +
geom_line(data = df, aes(x = date, y = deceased, color = 'deceased'))
# plot search trend

#ggplot() +
geom_line(data = df, aes(x = date, y = coronavirus, color = 'ppl search for coronavirus'))

ggplot() +
geom_line(data = df, aes(x = date, y = flu, color = 'ppl search for flu'))
```
plot a new graph contains of scaled graph and search trend
```{r}
normalize <- function(x)
{
    return((x- mean(x)) /sd(x))
}
norm_case = normalize(df$confirmed)
norm_cov19 = normalize(df$coronavirus)
ggplot() +
ggtitle("confirmed case against keyword searched (scaled)")+
geom_line(data = df, aes(x = date, y = norm_case, color = 'confirmed case'))+
geom_line(data = df, aes(x = date, y = norm_cov19, color = 'ppl search for coronavirus'))+
labs(y='')
#geom_line(data = df, aes(x = date, y = cold, color = 'ppl search for cold'))+
#geom_line(data = df, aes(x = date, y = pneumonia, color = 'ppl search for pneumonia'))+
#geom_line(data = df, aes(x = date, y = flu, color = 'ppl search for flu'))

```

realize policy is not a good indicator
create a new df without policy
```{r}
case_search_df = merge(case, search_trend, by.x='date', by.y='date')
# non cumulative
case_search_df$confirmed = c(0, diff(case_search_df$confirmed))
case_search_df$test = c(0, diff(case_search_df$test))
case_search_df$deceased = c(0, diff(case_search_df$deceased))
case_search_df$negative = c(0, diff(case_search_df$negative))
case_search_df$released = c(0, diff(case_search_df$released))

```

correlation 
```{r}
corr_df = as.data.frame(cbind(df$confirmed, df$coronavirus, df$cold, df$pneumonia, df$flu, df$policy_id))
colnames(corr_df) = c('confirmed', 'keyword_covid19', 'keyword_cold','keyword_pneumonia','keyword_flu', 'gov_policy')
corr = cor(corr_df)
#plot the matrix
par(mar=c(5.1, 4.1, 4.1, 4.1)) # adapt margins
plot(corr, digits=4, cex=1, col=topo.colors)

```

do a linear regression and see how they weighted
```{r}
lin_reg_keywords = lm(confirmed ~ ., data = corr_df)
summary(lin_reg_keywords)
vip::vip(lin_reg_keywords)
# #step(lin_reg_keywords)
# new_keywords_linreg = lm(formula = confirmed ~ keyword_covid19 + keyword_flu, data = corr_df)
# summary(new_keywords_linreg)
# vip::vip(new_keywords_linreg)
```

correlation between time and age
```{r}
timeage_df = timeage[,c(-2,-5)]
timeage_df$date = as.Date(timeage_df$date)
timeage_df = as.data.frame(split(timeage_df, timeage_df$age))
timeage_df = data.frame(timeage_df$X0s.date, timeage_df$X0s.confirmed, timeage_df$X10s.confirmed, timeage_df$X20s.confirmed, timeage_df$X30s.confirmed, timeage_df$X40s.confirmed, timeage_df$X50s.confirmed, timeage_df$X60s.confirmed, timeage_df$X70s.confirmed, timeage_df$X80s.confirmed)
colnames(timeage_df) = c('date', 'confirmed_0s', 'confirmed_10s', 'confirmed_20s', 'confirmed_30s', 'confirmed_40s', 'confirmed_50s', 'confirmed_60s', 'confirmed_70s', 'confirmed_80s')
rownames(timeage_df) = timeage_df$date
age_confirm_corr = cor(timeage_df[,-1])
#plot the graph
#non cumulation
time_non_cumu = data.frame(timeage_df$date[-1], apply(timeage_df[,-1], 2, diff))
colnames(time_non_cumu) = c('date', 'confirmed_0s', 'confirmed_10s', 'confirmed_20s', 'confirmed_30s', 'confirmed_40s', 'confirmed_50s', 'confirmed_60s', 'confirmed_70s', 'confirmed_80s')
```

plot the corr
```{r}
#plot the matrix
par(mar=c(5.1, 4.1, 4.1, 4.1)) # adapt margins
plot(age_confirm_corr, digits=4, cex=0.6, col=topo.colors)
```

time age death
```{r}
timeage = read.csv(paste0(file_path, '/Timeage.csv'), stringsAsFactors = FALSE, row.names=NULL)
timeage_death_df = timeage
timeage_death_df = as.data.frame(split(timeage_death_df, timeage_death_df$age))

timeage_death_df = data.frame(timeage_death_df$X0s.date, timeage_death_df$X0s.deceased, timeage_death_df$X10s.deceased, timeage_death_df$X20s.deceased, timeage_death_df$X30s.deceased, timeage_death_df$X40s.deceased, timeage_death_df$X50s.deceased, timeage_death_df$X60s.deceased, timeage_death_df$X70s.deceased, timeage_death_df$X80s.deceased)
colnames(timeage_death_df) = c('date', 'death_0s', 'death_10s', 'death_20s', 'death_30s', 'death_40s', 'death_50s', 'death_60s', 'death_70s', 'death_80s')
timeage_death_df$date = as.Date(timeage_death_df$date)
#non cumu
time_death_non_cumu = data.frame(timeage_death_df$date[-1], apply(timeage_death_df[,-1], 2, diff))
colnames(time_death_non_cumu) = c('date', 'death_0s', 'death_10s', 'death_20s', 'death_30s', 'death_40s', 'death_50s', 'death_60s', 'death_70s', 'death_80s')
```

time gen
```{r}
timegen_df = as.data.frame(split(timegen, timegen$sex))
timegen_confirm_df = data.frame(timegen_df$female.date, timegen_df$female.confirmed, timegen_df$male.confirmed)
colnames(timegen_confirm_df) = c('date', 'female', 'male')
timegen_confirm_df$date = as.Date(timegen_confirm_df$date)
#non cumu
timegen_confirm_noncumu_df = data.frame(timegen_confirm_df$date[-1], apply(timegen_confirm_df[,-1], 2, diff))
colnames(timegen_confirm_noncumu_df) = c('date', 'confirmed_female', 'confirmed_male')
```

time gen death
```{r}
timegen_df = as.data.frame(split(timegen, timegen$sex))
timegen_death_df = data.frame(timegen_df$female.date, timegen_df$female.deceased, timegen_df$male.deceased)
colnames(timegen_death_df) = c('date', 'female', 'male')
timegen_death_df$date = as.Date(timegen_death_df$date)
#non cumu
timegen_death_noncumu_df = data.frame(timegen_death_df$date[-1], apply(timegen_death_df[,-1], 2, diff))
colnames(timegen_death_noncumu_df) = c('date', 'death_female', 'death_male')
```

plot time gen
```{r}
df = timegen_death_noncumu_df
ggplot() + 
geom_line(data = df, aes(x = date, y = death_female, color = 'female')) + 
geom_line(data = df, aes(x = date, y = death_male, color = 'male'))+
ggtitle('death cases against gender')+
ylab('')
```


plot the graph
```{r}
df = time_death_non_cumu
ggplot() +
  
# geom_line(data = df, aes(x = date, y = death_0s, color = '0s')) +
# geom_line(data = df, aes(x = date, y = death_10s, color = '10s'))+
# geom_line(data = df, aes(x = date, y = death_20s, color = '20s'))+
# geom_line(data = df, aes(x = date, y = death_30s, color = '30s'))+
# geom_line(data = df, aes(x = date, y = death_40s, color = '40s'))+
geom_line(data = df, aes(x = date, y = death_50s, color = '50s'))+
geom_line(data = df, aes(x = date, y = death_60s, color = '60s'))+
geom_line(data = df, aes(x = date, y = death_70s, color = '70s'))+
geom_line(data = df, aes(x = date, y = death_80s, color = '80s'))+

ylab('')+
ggtitle('death cases against each age group (50, 60, 70, 80)')
```

scale it to see if there is any difference
```{r}
normalize <- function(x)
{
    return((x- mean(x)) /sd(x))
}
timeage_stand_df = apply(timeage_df[,2:ncol(timeage_df)], 2, normalize)
timeage_stand_df = data.frame(timeage_df[,1], timeage_stand_df)
timeage_stand_df[,1] = anytime::anydate(timeage_stand_df[,1])
colnames(timeage_stand_df)[1] = 'date'
```

```{r}
df = timeage_stand_df
ggplot() +
geom_line(data = df, aes(x = date, y = confirmed_0s, color = '0s')) +
geom_line(data = df, aes(x = date, y = confirmed_10s, color = '10s'))+
geom_line(data = df, aes(x = date, y = confirmed_20s, color = '20s'))+
geom_line(data = df, aes(x = date, y = confirmed_30s, color = '30s'))+
geom_line(data = df, aes(x = date, y = confirmed_40s, color = '40s'))+
geom_line(data = df, aes(x = date, y = confirmed_50s, color = '50s'))+
geom_line(data = df, aes(x = date, y = confirmed_60s, color = '60s'))+
geom_line(data = df, aes(x = date, y = confirmed_70s, color = '70s'))+
geom_line(data = df, aes(x = date, y = confirmed_80s, color = '80s'))+

ylab('')
```



split the rows of TimeProvince
```{r}
province$province = as.factor(province$province)
province_list = split(province, province$province)
province_df = as.data.frame(province_list)

pro_df = cbind(province_df$Busan.date, 
province_df$Busan.confirmed, 
province_df$Chungcheongbuk.do.confirmed, 
province_df$Chungcheongnam.do.confirmed,
province_df$Daegu.confirmed,
province_df$Daejeon.confirmed,
province_df$Gangwon.do.confirmed,
province_df$Gwangju.confirmed,
province_df$Gyeonggi.do.confirmed,
province_df$Gyeongsangbuk.do.confirmed,
province_df$Gyeongsangnam.do.confirmed,
province_df$Incheon.confirmed,
province_df$Jeju.do.confirmed,
province_df$Jeollabuk.do.confirmed,
province_df$Jeollanam.do.confirmed,
province_df$Sejong.confirmed,
province_df$Seoul.confirmed,
province_df$Ulsan.confirmed)

temp = as.data.frame(apply(pro_df[,2:ncol(pro_df)], 2, as.numeric))
colnames(temp) = c('Busan', 'Chungcheongbuk', 'Chungcheongnam', 'Daegu', 'Daejeon', 'Gangwon','Gwangju', 'Gyeonggi', 'Gyeongsangbuk', 'Gyeongsangnam', 'Incheon', 'Jeju', 'Jeollabuk', 'Jeollanam', 'Sejong', 'Seoul', 'Ulsan')
pro_df = data.frame(province_df$Busan.date, temp)
colnames(pro_df)[1] = 'date'
#convert datetime
pro_df[,1] = anytime::anydate(pro_df[,1])
#non cumulation
pro_noncum_df = data.frame(pro_df$date[-1], apply(pro_df[,-1], 2, diff))
colnames(pro_noncum_df) = c('date', 'Busan', 'Chungcheongbuk', 'Chungcheongnam', 'Daegu', 'Daejeon', 'Gangwon','Gwangju', 'Gyeonggi', 'Gyeongsangbuk', 'Gyeongsangnam', 'Incheon', 'Jeju', 'Jeollabuk', 'Jeollanam', 'Sejong', 'Seoul', 'Ulsan')

```

standardize it by min-max scales
```{r}
normalize <- function(x)
{
    return((x- min(x)) /(max(x)-min(x)))
}
pro_stand_df = apply(pro_df[,2:ncol(pro_df)], 2, normalize)
pro_stand_df = data.frame(pro_df[,1], pro_stand_df)
pro_stand_df[,1] = anytime::anydate(pro_stand_df[,1])
colnames(pro_stand_df)[1] = 'date'
```


standardize it by x-min/sd
```{r}
normalize <- function(x)
{
    return((x- mean(x)) /sd(x))
}
pro_stand_df = apply(pro_df[,2:ncol(pro_df)], 2, normalize)
pro_stand_df = data.frame(pro_df[,1], pro_stand_df)
pro_stand_df[,1] = anytime::anydate(pro_stand_df[,1])
colnames(pro_stand_df)[1] = 'date'
```


plot TimeProvince
```{r, fig.width = 8, fig.height = 8}
df = pro_stand_df
ggplot() + 
geom_line(data = df, aes(x = date, y = Busan, color = 'Busan')) + 
geom_line(data = df, aes(x = date, y = Chungcheongbuk, color = 'Chungcheongbuk'))+ 
geom_line(data = df, aes(x = date, y = Chungcheongnam, color = 'Chungcheongnam'))+
geom_line(data = df, aes(x = date, y = Daegu, color = 'Daegu'))+
geom_line(data = df, aes(x = date, y = Daejeon, color = 'Daejeon'))+
geom_line(data = df, aes(x = date, y = Gangwon, color = 'Gangwon'))+
geom_line(data = df, aes(x = date, y = Gwangju, color = 'Gwangju'))+
geom_line(data = df, aes(x = date, y = Gyeonggi, color = 'Gyeonggi'))+
geom_line(data = df, aes(x = date, y = Gyeongsangbuk, color = 'Gyeongsangbuk'))+
geom_line(data = df, aes(x = date, y = Gyeongsangnam, color = 'Gyeongsangnam'))+
geom_line(data = df, aes(x = date, y = Incheon, color = 'Incheon'))+
geom_line(data = df, aes(x = date, y = Jeju, color = 'Jeju'))+
geom_line(data = df, aes(x = date, y = Jeollabuk, color = 'Jeollabuk'))+
geom_line(data = df, aes(x = date, y = Jeollanam, color = 'Jeollanam'))+
geom_line(data = df, aes(x = date, y = Sejong, color = 'Sejong'))+
geom_line(data = df, aes(x = date, y = Seoul, color = 'Seoul'))+
geom_line(data = df, aes(x = date, y = Ulsan, color = 'Jeollabuk'))+
ggtitle("cumulative confirmed case within each province")
ylab('')
```

Only plot the graph with the 4 country with most confirmed case
(without standardization)
```{r}
df = pro_df
ggplot() + 
geom_line(data = df, aes(x = date, y = Seoul, color = 'Seoul'))+
geom_line(data = df, aes(x = date, y = Daegu, color = 'Daegu'))+
geom_line(data = df, aes(x = date, y = Gyeonggi, color = 'Gyeonggi'))+
geom_line(data = df, aes(x = date, y = Gyeongsangbuk, color = 'Gyeongsangbuk'))+
  ggtitle('cumulative confirmed case within the 4 most severe province')+
  ylab('')
```

```{r}
df = pro_stand_df
ggplot() + 
geom_line(data = df, aes(x = date, y = Seoul, color = 'Seoul'))+
geom_line(data = df, aes(x = date, y = Daegu, color = 'Daegu'))+
geom_line(data = df, aes(x = date, y = Gyeonggi, color = 'Gyeonggi'))+
geom_line(data = df, aes(x = date, y = Gyeongsangbuk, color = 'Gyeongsangbuk'))+
    ggtitle('cumulative confirmed case within the 4 most severe province (scaled)')+
  ylab('')
```
correlation of only this 4 country
```{r}
corr_4_df = data.frame(pro_df$Seoul, pro_df$Daegu, pro_df$Gyeonggi, pro_df$Gyeongsangbuk)
colnames(corr_4_df) = c('Seoul', 'Daegu', 'Gyeonggi', 'Gyeongsangbuk')
corr_4 = cor(corr_4_df)
```

find the correlation of the interesting factor
(move the place)
```{r}

corr_pro = cor(pro_df[,2:ncol(pro_df)])
#plot the matrix
par(mar=c(5.1, 4.1, 4.1, 4.1)) # adapt margins
plot(corr_pro, digits=4, cex=0.5, col=topo.colors)
```

train model? search for models
First use the non-time series model
data cleaning

call the data frame back
```{r}
time_non_cumu
time_death_non_cumu
case_search_df$date = as.Date(case_search_df$date)
timegen_death_noncumu_df
timegen_confirm_noncumu_df
pro_noncum_df
```

merge df
```{r}
df = merge(time_non_cumu, time_death_non_cumu, by = 'date')
df = merge(df, timegen_death_noncumu_df, by = 'date')
df = merge(df, timegen_confirm_noncumu_df, by = 'date')
df = merge(df, case_search_df, by = 'date')
df = df[,-24]

df$tmr_confirmed = data.table::shift(df$confirmed, n = -1)
```

corr and whole model
```{r}
corr = cor(df[,-1])
lin_reg = lm(tmr_confirmed ~ ., data = df)
summary(lin_reg)
```

split the model into training and testing data
```{r}
date = df$date
set.seed(4011)
ind = 1:as.integer(nrow(df)*0.7)
#ind <- sample(seq_len(nrow(df)), size = nrow(df)*0.7)
rownames(df) = df$date
df = df[-nrow(df),-1]

train <- df[ind, ]
test <- df[-ind, ]
train = na.omit(train)
test = na.omit(test)

train_y = train$tmr_confirmed
train_x = train[,-ncol(train)]
test_y = test$tmr_confirmed
test_x = test[,-ncol(test)]
train_date = date[ind]
test_date = date[-ind]
```


```{r}
lin_reg = lm(tmr_confirmed ~ ., data = train)
summary(lin_reg)
predicted = predict(lin_reg, test)
result = rmse(test$tmr_confirmed, as.numeric(predicted))
result
step(lin_reg)
lin_reg_AIC = lm(formula = tmr_confirmed ~ + confirmed_0s + confirmed_10s + 
    confirmed_20s + confirmed_30s + confirmed_40s + confirmed_50s + 
    confirmed_60s + confirmed_70s + confirmed_80s + death_50s + 
    death_80s + confirmed_female + confirmed_male + test + negative + 
    coronavirus, data = train)
summary(lin_reg_AIC)
predicted = predict(lin_reg_AIC, test)
result = rmse(test$tmr_confirmed, as.numeric(predicted))
result
```

random forest
```{r}
rf_classifier = randomForest(tmr_confirmed ~ ., data = train, ntree=500, mtry=10, importance=TRUE)
#plot the model
plot(rf_classifier)

predicted = predict(rf_classifier, test)
result = rmse(test$tmr_confirmed, as.numeric(predicted))
result

#tune params
#as we know, it converges when number of trees > 100
#we only tune mtry
rf_1 = tuneRF(x = train_x, y = train_y, mtryStart = 5, ntreeTry = 500 ,stepFactor = 1.5, improve = 0.01, trace = FALSE)
#use the new params
rf_classifier = randomForest(tmr_confirmed ~ ., data = train, ntree=500, mtry=5, importance=TRUE)
predicted = predict(rf_classifier, test)
result = rmse(test$tmr_confirmed, as.numeric(as.integer(predicted)))
result
#we can see there is a slight increase in our model
#plot the result
test_date = cbind(test, predicted, rownames(test))
colnames(test_date)[ncol(test_date)] = 'date'
test_date$date = as.Date(test_date$date)

ggplot() + 
geom_line(data = test_date, aes(x = date,y= tmr_confirmed
, color = 'confirmed case')) + 
geom_line(data = test_date, aes(x = date, y = predicted, color = 'prediction result'))+
  ylab('')+
  ggtitle("true reuslt compare to predicted resuly (random forest)")
#vip
vip::vip()
```

xgboost
```{r}
set.seed(4011)


dtrain <- xgb.DMatrix(data = as.matrix(train_x), label=as.matrix(train_y))
dtest <- xgb.DMatrix(data = as.matrix(test_x), label=as.matrix(test_y))


xgb.fit1 <- xgb.cv(
data = dtrain,
nrounds = 1000,
nfold = 5,
objective = "reg:linear",  # for regression models
verbose = 0
#early_stopping_rounds = 10# silent
)

print(xgb.fit1,verbose = TRUE)
xgb.fit1$evaluation_log

xgb.fit1$evaluation_log %>%
  dplyr::summarise(
    ntrees.train = which(train_rmse_mean == min(train_rmse_mean))[1],
    rmse.train   = min(train_rmse_mean),
    ntrees.test  = which(test_rmse_mean == min(test_rmse_mean))[1],
    rmse.test   = min(test_rmse_mean)
  )

ggplot(xgb.fit1$evaluation_log) +
  geom_line(aes(iter, train_rmse_mean), color = "red") +
  geom_line(aes(iter, test_rmse_mean), color = "blue")
```

add some features
```{r}
set.seed(4011)

xgb.fit2 <- xgb.cv(
data = dtrain,
nrounds = 1000,
nfold = 5,
objective = "reg:linear",  # for regression models
verbose = 0,
early_stopping_rounds = 10,
gamma = 100
)

ggplot(xgb.fit2$evaluation_log) +
  geom_line(aes(iter, train_rmse_mean), color = "red") +
  geom_line(aes(iter, test_rmse_mean), color = "blue")
```

tune the params
```{r}
  params <- list(
    eta = .1,
    max_depth = 5,
    min_child_weight = 2,
    subsample = .8,
    colsample_bytree = .9
  )

set.seed(4011)
system.time(
xgb.fit3 <- xgb.cv(
  params = params,
  data = dtrain,
  nrounds = 1000,
  nfold = 5,
  objective = "reg:squarederror",  # for regression models
  verbose = T,               # silent,
  early_stopping_rounds = 10 # stop if no improvement for 10 consecutive trees
)
)



# assess results
xgb.fit3$evaluation_log %>%
  dplyr::summarise(
    ntrees.train = which(train_rmse_mean == min(train_rmse_mean))[1],
    rmse.train   = min(train_rmse_mean),
    ntrees.test  = which(test_rmse_mean == min(test_rmse_mean))[1],
    rmse.test   = min(test_rmse_mean)
  )
```
perform grid search
```{r}
# create hyperparameter grid
hyper_grid <- expand.grid(
  eta = c(.01, .05, .1, .3),
  max_depth = c(1, 3, 5, 7),
  min_child_weight = c(1, 3, 5, 7),
  subsample = c(.65, .8, 1), 
  colsample_bytree = c(.8, .9, 1),
  optimal_trees = 0,               # a place to dump results
  min_RMSE = 0 ,                    # a place to dump results
  gamma = c(0, 5, 10, 15, 20)
)
 
nrow(hyper_grid)
```

```{r}
for(i in 1:nrow(hyper_grid)) {
 
  # create parameter list
  params <- list(
    eta = hyper_grid$eta[i],
    max_depth = hyper_grid$max_depth[i],
    min_child_weight = hyper_grid$min_child_weight[i],
    subsample = hyper_grid$subsample[i],
    colsample_bytree = hyper_grid$colsample_bytree[i]
  )
 
  # reproducibility
  set.seed(4011)
 
  # train model
  xgb.tune <- xgb.cv(
    params = params,
    data = dtrain,
    nrounds = 5000,
    nfold = 5,
    objective = "reg:squarederror",  # for regression models
    verbose = 0,               # silent,
    early_stopping_rounds = 10, # stop if no improvement for 10 consecutive trees
  )
 
  # add min training error and trees to grid
  hyper_grid$optimal_trees[i] <- which.min(xgb.tune$evaluation_log$test_rmse_mean)
  hyper_grid$min_RMSE[i] <- min(xgb.tune$evaluation_log$test_rmse_mean)
  print(paste('optimal trees:', hyper_grid$optimal_trees[i]))
  print(paste('min RMSE:', hyper_grid$min_RMSE[i]))
  print('----------------------')
}
 
hyper_grid %>%
  dplyr::arrange(min_RMSE) %>%
  head(10)
```


```{r}
params <- list(
  eta = 0.3,
  max_depth = 5,
  min_child_weight = 1,
  subsample = 0.8,
  colsample_bytree = 0.9,
  optimal_trees = 13
)

xgb.fit.final <- xgboost(
  params = params,
  data = as.matrix(train_x),
  label = train_y,
  nrounds = 20,
  objective = "reg:linear",
  verbose = 0
)


predicted = predict(xgb.fit.final, dtest)
result = rmse(test$tmr_confirmed, as.numeric(predicted))

test_date = cbind(test, predicted, rownames(test))
colnames(test_date)[ncol(test_date)] = 'date'
test_date$date = as.Date(test_date$date)


ggplot() + 
geom_line(data = test_date, aes(x = date,y= tmr_confirmed
, color = 'confirmed case')) + 
geom_line(data = test_date, aes(x = date, y = predicted, color = 'prediction result'))+
  ylab('')+
  ggtitle("true reuslt compare to predicted result (XGboost)")
#plot vip
importance_matrix <- xgb.importance(model = xgb.fit.final)
xgb.plot.importance(importance_matrix, top_n = 10, measure = "Gain")
```

